### 2021-10-13 plos_latex_template.tex
adding an suggestion of alt.tex for the figure
adding the figure's png, caption and alt text (unsuccessfully)

@@

% Rocío: Main message of the paragraph: Roadmap of the paper
The rules written here are directed to people who are part of a stable meetings committee that oversees the site/location selection process, or that coordinates with the local organizers of conferences.
The rules can also be helpful to local/virtual organizers who desire to make an inclusive conference starting at the planning stage.
These tips stem from the authors' experience of organizing useR! 2021, a virtual and global statistical computing conference for users and developers of the R programming language \cite{r_core_team_2021}. 
We embraced the challenge of organizing a high-quality virtual conference in the context of the COVID-19 pandemic and making it a kind, inclusive, and accessible experience for everyone. 
Here, we share the lessons learned within the past year of organizing this global useR! 2021, summarized as ten simple rules towards an inclusive conference.
We have organized these rules in three groups.
Rules 1, 2 and 10 refer to pillars of an inclusive conference: embracing diversity in all its dimensions, creating a safe and welcoming environment for everyone, and making the conference part of a long-term process for inclusion.
The next two rules are focused on the people that participate in the conference: 
Rule 3 refers to the importance of working with an inclusive and diverse organizing team, and Rule 4 concerns the necessity of removing implicit and systemic bias from spotlight roles like keynote speakers, other presenters, program committee members, or other session chairs. 
Rules 5 to 9 are rules about actions regarding components of the conference that should be carefully planned for: an online component, accessibility to people with disabilities, language inclusiveness, a welcoming communication strategy, and financial resources to support inclusion. 
These rules apply equally to academic, industry, or mixed conferences; the rules are inspired by a global experience but also apply at the regional or local level.
% Rocío: the last sentence was copied from the abstract because we need a closing sentence.
% Rocío: Could add a line introducing Fig. in https://docs.google.com/drawings/d/1iS1pLc9OldLMe_jhNT6OGIbT9s5KvlHpUoDd19vHkCY/edit?usp=sharing and the whole structure [x]

>>>>

%sara: for commenting the pdf to add alt text (if anyone knows a better solution for atl text please help)
\usepackage{pdfcomment}

@@

% Rocío: Main message of the paragraph: Roadmap of the paper
The rules written here are directed to people who are part of a stable meetings committee that oversees the site/location selection process, or that coordinates with the local organizers of conferences.
The rules can also be helpful to local/virtual organizers who desire to make an inclusive conference starting at the planning stage.
These tips stem from the authors' experience of organizing useR! 2021, a virtual and global statistical computing conference for users and developers of the R programming language \cite{r_core_team_2021}. 
We embraced the challenge of organizing a high-quality virtual conference in the context of the COVID-19 pandemic and making it a kind, inclusive, and accessible experience for everyone. 
Here, we share the lessons learned within the past year of organizing this global useR! 2021, summarized as ten simple rules towards an inclusive conference.
We have organized these rules in three groups (Figure \ref{fig:diagram}).
%sara: i think here is a good place to add the diagram: https://docs.google.com/drawings/d/1iS1pLc9OldLMe_jhNT6OGIbT9s5KvlHpUoDd19vHkCY/edit?usp=sharing
%sara: still need to better format figure size and get the alt text right :P
Rules 1, 2 and 10 refer to pillars of an inclusive conference: embracing diversity in all its dimensions, creating a safe and welcoming environment for everyone, and making the conference part of a long-term process for inclusion.
The next two rules are focused on the people that participate in the conference: 
Rule 3 refers to the importance of working with an inclusive and diverse organizing team, and Rule 4 concerns the necessity of removing implicit and systemic bias from spotlight roles like keynote speakers, other presenters, program committee members, or other session chairs. 
Rules 5 to 9 are rules about actions regarding components of the conference that should be carefully planned for: an online component, accessibility to people with disabilities, language inclusiveness, a welcoming communication strategy, and financial resources to support inclusion. 
These rules apply equally to academic, industry, or mixed conferences; the rules are inspired by a global experience but also apply at the regional or local level.
% Rocío: the last sentence was copied from the abstract because we need a closing sentence.
% Rocío: Could add a line introducing Fig. in https://docs.google.com/drawings/d/1iS1pLc9OldLMe_jhNT6OGIbT9s5KvlHpUoDd19vHkCY/edit?usp=sharing and the whole structure [x]

\begin{figure}[!h]
\centering
%sara: without success i'm trying to use pdfcomment package and pdftooltip to make the alt-text. any help?
\pdftooltip{
\includegraphics[width=\textwidth]{figs/10_rules_diversity.png}}{
%sara: suggestion for alt text:
Diagram of how the 10 rules are organized into three groups: grounding rules (rules 1, 2, and 10), people-related rules (rules 3 and 4), and design rules (rules 5 to 9). The diagram has five rows. Each line contains rectangular boxes with the rule number and a short title for each rule. Each rule box is colored based on their group (grounding rules are grey, people-related rules are green and design rules are pink). First row is for the grounding rules 1. Multidimensional diversity and 2. Safe and inclusive environment in grey boxes. Second row is for people-related rules 3. Organizing team and 4. Unbias in green boxes. Third row is for the design rules 5. Online component, 6. Accessibility for disabilities, 7. Language inclusivity in pink boxes. The fourth row is for the design rules 8. Communication and 9. Financial support and budget in pink boxes. The last row is for the grounding rule 10. Diversity and inclusion as a process in grey boxes.
}
\caption{Diagram of the rules organized in three groups: grounding rules (rules 1, 2, and 10), people-related rules (rules 3 and 4), and design rules (rules 5 to 9).}
\label{fig:diagram}
\end{figure}
